### 2024-03-31 paper/paper.qmd
Add files via upload

---
title: "STA302 Project"
subtitle: "What factors and how influence Ames Iowa Housing Sale Price"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: https://github.com/Yuki010305/Final-Paper."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: html
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(MASS)
library(magrittr)
library(gridExtra)
library(ggplot2)
library(car)
library(stargazer)
library(modelsummary)

```

# Introduction

The housing issue is a pillar industry of a country, and the healthy development of the housing issue affects the country's economic development level. In order to help the stable development of the housing transaction market, this project plans to better evaluate the value of housing transactions for Ames. So, the main purpose of this project is to explore the factors that influence the sale price of homes in Ames, Iowa, and how they affect the home sales price. The characteristics of the homes we selected include central air condition, car capacity of garage, general shape of property, rate of overall quality, total above ground living area, number of fireplaces and sale year. The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

```{r}
#| label: ames
#| fig-cap: ames house
#| echo: false
#current_dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
#setwd(current_dir)

ames_raw <- read.csv("../data/AmesHousing.csv")

```

The Raw data collects 82 features of the house, and data quality is not high.

```{r}
#| label: ames select variable
#| fig-cap: ames house save
#| echo: false
ames <- dplyr::select(ames_raw,'Central.Air', 'Lot.Shape', 'Garage.Cars', 'Overall.Qual', 'TotRms.AbvGrd', 'Gr.Liv.Area', 'Garage.Area', 'Fireplaces','Yr.Sold', 'SalePrice')
ames <- na.omit(ames)

write.csv(ames,"../data/analysis_data/ames_analysis.csv",row.names = FALSE)

```

```{r}
#| label: summary
#| fig-cap: summary numeric
#| echo: false
summary(ames[,-c(1,2)])
```

```{r}
#| label: air
#| fig-cap: central air table
#| echo: false
### Categorical table
table(ames$`Central.Air`)
prop.table(table(ames$`Central.Air`))
```

```{r}
#| label: lot
#| fig-cap: lot shape table
#| echo: false
table(ames$`Lot.Shape`)
prop.table(table(ames$`Lot.Shape`))
```

```{r}
#| label: histprice
#| fig-cap: sale price hist
#| echo: false
par(mfrow=c(1,2))
hist(ames$SalePrice, breaks=10, xlab="Sale Price",main="Sale price",col="red") 
hist(log(ames$SalePrice), breaks=10, xlab="log-transform Sale Price",main="Sale price",col="red") 
```

As you can see from the figure, house sales prices are right-skewed data. When building the model, we need to log-transform the house sales prices to make them conform to the normal distribution.

```{r}
#| label: histbox
#| fig-cap: hists
#| echo: false

par(mfrow=c(3,2))

hist(ames$Garage.Area, breaks=10,main="", xlab="Garage Area")
hist(ames$Gr.Liv.Area, breaks=10, main="",xlab="Above grade living area")

boxplot(ames$Overall.Qual,xlab="Overall Qual")
boxplot(ames$TotRms.AbvGrd, xlab="TotRms AbvGrd")

boxplot(ames$Fireplaces, xlab="Fireplaces")
```

```{r,warning=FALSE}
#| label: point
#| fig-cap: points
#| echo: false
a=ggplot(data=ames, aes(x=Garage.Area, y=SalePrice)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
  labs(x = 'Garage Area', y='Sale Price')+
  theme_bw()

b=ggplot(data=ames, aes(x=Gr.Liv.Area, y=SalePrice)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE,size=1.5) + 
  labs(x = 'Above grade living area square feet', y='Sale Price')+
  theme_bw()

grid.arrange(a,b, nrow=1)
```

The above scatter plot shows that both Garage Area and Above grade living area have a certain positive impact on sale price, especially the positive correlation between Above grade living area and sale price is very strong.

# Model

## Model set-up

After data processing, the data set is a clean data set with 2929 observations and 10 house characteristic variables. In order to evaluate the performance of the model, we randomly split the analysis data set into a test set and a training set in a ratio of 75%:25%.

```{r}
#| label: spilt
#| fig-cap: spilt data
#| echo: false
#| 
set.seed(123456)
rows <- sample(1:round(0.75*nrow(ames)), replace=FALSE) 
train<- ames[rows,]
test=ames[-rows,]
```

The first model we build is the full model. We then improve the model by removing insignificant variables.

```{r}
#| label: full
#| fig-cap: full model
#| echo: false
#| 
### full model
full = lm(log(SalePrice) ~ ., data = train)
summary(full)
```

```{r}
#| label: sub
#| fig-cap: sub model
#| echo: false
#| 
ml = lm(log(SalePrice) ~ .-TotRms.AbvGrd-Yr.Sold, data = train)
summary(ml)
```

```{r}
#| label: ftest
#| fig-cap: F test
#| echo: false

# F test
anova(ml,full)
```

Analyzing the model of full and significant variables through the Partial F test, we found that the p value is much greater than 0, which shows that we cannot reject the null hypothesis and there is not much difference in the performance of the two models. But in terms of the number of variables, we still choose the model with significant variables.

```{r}
#| label: plot1
#| fig-cap: plot model
#| echo: false
par(mfrow=c(2,2))

plot(ml)
```

The residual test found that both ends of the QQ graph deviated greatly from the straight line and were affected by special points such as outliers and leverage points. So, in order to further improve the performance of model fitting, we will delete special points from the training set.

```{r}
#| label: outlier
#| fig-cap: remove outliers
#| echo: false

# determine whether there are leverage points
n <- nrow(train)
p <- length(coef(ml))-1
# leverage cutoff
h_cut <- 2*(p+1)/n 
off = which(hatvalues(ml) > h_cut)
new_train = train[-off,]
```

After deleting special points such as level points, a new model was refitted.

```{r}
#| label: model2
#| fig-cap: create model 2
#| echo: false
#| 
ml_new = lm(log(SalePrice) ~ .-TotRms.AbvGrd-Yr.Sold, data =new_train)
summary(ml_new)
```

```{r}
#| label: savemodel
#| fig-cap: save model
#| echo: false
#| 
saveRDS(ml_new, "../model/model.rds")
```

### Model justification

```{r}
#| label: plotmodel2
#| fig-cap: plot model 2
#| echo: false
par(mfrow=c(2,2))
plot(ml_new)
```

Clearly the model has improved.

#### A1:Linearity of the Relationship

```{r}
#| label: plothat
#| fig-cap: plot y hat
#| echo: false
#| 
plot(new_train$SalePrice ~ exp(fitted(ml_new)), main="Y versus Y-hat", xlab="Y-hat", ylab="Y")
abline(a = 0, b = 1)
lines(lowess(new_train$SalePrice ~ exp(fitted(ml_new))), lty=2)
```

The above scatter plot fits the relationship between the predicted value and the actual value. You can see that these points are almost on or close to the line, so we can say that a linear relationship is satisfied.

#### A2.Covariance of Errors

#### A3.Common Error variance

homoskedasticity

#### A4. Normality of Error

# Results

```{r}
#| echo: false
#| label: read
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

model <-
  readRDS(file = ("../model/model.rds"))

summary(model)
#stargazer(model, type="latex",
#          dep.var.labels=c("Log Sale Price"), align = TRUE)
```

1. When other factors remain unchanged, having central air conditioning increases the sales price of a house by 16.22%.

# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

\newpage

# References

### 2024-03-31 paper/paper.tex
Add files via upload

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={STA302 Project},
  pdfauthor={First author; Another author},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{STA302 Project\thanks{Code and data are available at:
https://github.com/Yuki010305/Final-Paper.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{What factors and how influence Ames Iowa Housing Sale Price}
\author{First author \and Another author}
\date{March 31, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}

\section{Introduction}\label{introduction}

The housing issue is a pillar industry of a country, and the healthy
development of the housing issue affects the country's economic
development level. In order to help the stable development of the
housing transaction market, this project plans to better evaluate the
value of housing transactions for Ames. So, the main purpose of this
project is to explore the factors that influence the sale price of homes
in Ames, Iowa, and how they affect the home sales price. The
characteristics of the homes we selected include central air condition,
car capacity of garage, general shape of property, rate of overall
quality, total above ground living area, number of fireplaces and sale
year. The remainder of this paper is structured as follows.
Section~\ref{sec-data}\ldots.

\section{Data}\label{sec-data}

\begin{verbatim}
  Garage.Cars     Overall.Qual    TotRms.AbvGrd     Gr.Liv.Area  
 Min.   :0.000   Min.   : 1.000   Min.   : 2.000   Min.   : 334  
 1st Qu.:1.000   1st Qu.: 5.000   1st Qu.: 5.000   1st Qu.:1126  
 Median :2.000   Median : 6.000   Median : 6.000   Median :1442  
 Mean   :1.767   Mean   : 6.095   Mean   : 6.443   Mean   :1500  
 3rd Qu.:2.000   3rd Qu.: 7.000   3rd Qu.: 7.000   3rd Qu.:1742  
 Max.   :5.000   Max.   :10.000   Max.   :15.000   Max.   :5642  
  Garage.Area       Fireplaces        Yr.Sold       SalePrice     
 Min.   :   0.0   Min.   :0.0000   Min.   :2006   Min.   : 12789  
 1st Qu.: 320.0   1st Qu.:0.0000   1st Qu.:2007   1st Qu.:129500  
 Median : 480.0   Median :1.0000   Median :2008   Median :160000  
 Mean   : 472.8   Mean   :0.5995   Mean   :2008   Mean   :180806  
 3rd Qu.: 576.0   3rd Qu.:1.0000   3rd Qu.:2009   3rd Qu.:213500  
 Max.   :1488.0   Max.   :4.0000   Max.   :2010   Max.   :755000  
\end{verbatim}

\begin{verbatim}

   N    Y 
 196 2733 
\end{verbatim}

\begin{verbatim}

         N          Y 
0.06691704 0.93308296 
\end{verbatim}

\begin{verbatim}

 IR1  IR2  IR3  Reg 
 979   76   16 1858 
\end{verbatim}

\begin{verbatim}

        IR1         IR2         IR3         Reg 
0.334243769 0.025947422 0.005462615 0.634346193 
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/histprice-1.pdf}

}

\caption{sale price hist}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/histbox-1.pdf}

}

\caption{hists}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/histbox-2.pdf}

}

\caption{hists}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/histbox-3.pdf}

}

\caption{hists}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/histbox-4.pdf}

}

\caption{hists}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/histbox-5.pdf}

}

\caption{hists}

\end{figure}%

\begin{verbatim}
`geom_smooth()` using formula = 'y ~ x'
`geom_smooth()` using formula = 'y ~ x'
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/point-1.pdf}

}

\caption{points}

\end{figure}%

\section{Model}\label{model}

\subsection{Model set-up}\label{model-set-up}

\begin{verbatim}

Call:
lm(formula = log(SalePrice) ~ ., data = train)

Residuals:
     Min       1Q   Median       3Q      Max 
-1.70702 -0.09049  0.01101  0.10726  0.70988

Coefficients:
                Estimate Std. Error t value Pr(>|t|)    
(Intercept)    1.817e+01  7.482e+00   2.429  0.01523 *  
Central.AirY   2.232e-01  1.674e-02  13.334  < 2e-16 ***
Lot.ShapeIR2   5.908e-02  2.524e-02   2.341  0.01932 *  
Lot.ShapeIR3  -1.409e-01  5.068e-02  -2.781  0.00547 ** 
Lot.ShapeReg  -4.995e-02  8.550e-03  -5.841 5.95e-09 ***
Garage.Cars    6.232e-02  1.132e-02   5.502 4.18e-08 ***
Overall.Qual   1.393e-01  3.886e-03  35.854  < 2e-16 ***
TotRms.AbvGrd -1.477e-03  4.271e-03  -0.346  0.72961    
Gr.Liv.Area    2.032e-04  1.556e-05  13.056  < 2e-16 ***
Garage.Area    1.532e-04  3.906e-05   3.922 9.06e-05 ***
Fireplaces     5.108e-02  6.997e-03   7.300 4.00e-13 ***
Yr.Sold       -3.828e-03  3.725e-03  -1.028  0.30418    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.18 on 2185 degrees of freedom
Multiple R-squared:  0.8055,    Adjusted R-squared:  0.8045 
F-statistic: 822.7 on 11 and 2185 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{verbatim}

Call:
lm(formula = log(SalePrice) ~ . - TotRms.AbvGrd - Yr.Sold, data = train)

Residuals:
     Min       1Q   Median       3Q      Max 
-1.71281 -0.08994  0.01188  0.10828  0.71389

Coefficients:
               Estimate Std. Error t value Pr(>|t|)    
(Intercept)   1.048e+01  2.337e-02 448.365  < 2e-16 ***
Central.AirY  2.237e-01  1.672e-02  13.375  < 2e-16 ***
Lot.ShapeIR2  5.990e-02  2.519e-02   2.378  0.01751 *  
Lot.ShapeIR3 -1.390e-01  5.063e-02  -2.745  0.00609 ** 
Lot.ShapeReg -5.012e-02  8.547e-03  -5.864 5.22e-09 ***
Garage.Cars   6.200e-02  1.128e-02   5.497 4.32e-08 ***
Overall.Qual  1.396e-01  3.859e-03  36.171  < 2e-16 ***
Gr.Liv.Area   1.993e-04  9.991e-06  19.943  < 2e-16 ***
Garage.Area   1.548e-04  3.883e-05   3.988 6.89e-05 ***
Fireplaces    5.109e-02  6.970e-03   7.330 3.23e-13 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.1799 on 2187 degrees of freedom
Multiple R-squared:  0.8054,    Adjusted R-squared:  0.8046 
F-statistic:  1006 on 9 and 2187 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{verbatim}
Analysis of Variance Table

Response: log(SalePrice)
               Df  Sum Sq Mean Sq  F value    Pr(>F)    
Central.Air     1  52.013  52.013 1606.576 < 2.2e-16 ***
Lot.Shape       3  24.594   8.198  253.216 < 2.2e-16 ***
Garage.Cars     1 110.945 110.945 3426.882 < 2.2e-16 ***
Overall.Qual    1  84.906  84.906 2622.578 < 2.2e-16 ***
Gr.Liv.Area     1  18.416  18.416  568.825 < 2.2e-16 ***
Garage.Area     1   0.458   0.458   14.156 0.0001727 ***
Fireplaces      1   1.739   1.739   53.722 3.234e-13 ***
Residuals    2187  70.804   0.032                       
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plot1-1.pdf}

}

\caption{plot model}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plot1-2.pdf}

}

\caption{plot model}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plot1-3.pdf}

}

\caption{plot model}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plot1-4.pdf}

}

\caption{plot model}

\end{figure}%

\begin{verbatim}

Call:
lm(formula = log(SalePrice) ~ . - TotRms.AbvGrd - Yr.Sold, data = new_train)

Residuals:
     Min       1Q   Median       3Q      Max 
-1.04702 -0.08837  0.01205  0.10368  0.72952

Coefficients:
               Estimate Std. Error t value Pr(>|t|)    
(Intercept)   1.052e+01  2.629e-02 399.959  < 2e-16 ***
Central.AirY  1.622e-01  2.087e-02   7.771 1.23e-14 ***
Lot.ShapeReg -4.749e-02  7.957e-03  -5.968 2.83e-09 ***
Garage.Cars   3.296e-02  1.230e-02   2.679  0.00744 ** 
Overall.Qual  1.319e-01  3.806e-03  34.657  < 2e-16 ***
Gr.Liv.Area   2.276e-04  1.064e-05  21.382  < 2e-16 ***
Garage.Area   3.237e-04  4.289e-05   7.547 6.73e-14 ***
Fireplaces    5.164e-02  6.616e-03   7.805 9.47e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.1623 on 2009 degrees of freedom
Multiple R-squared:  0.8228,    Adjusted R-squared:  0.8222 
F-statistic:  1332 on 7 and 2009 DF,  p-value: < 2.2e-16
\end{verbatim}

\subsubsection{Model justification}\label{model-justification}

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plotmodel2-1.pdf}

}

\caption{plot model 2}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plotmodel2-2.pdf}

}

\caption{plot model 2}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plotmodel2-3.pdf}

}

\caption{plot model 2}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plotmodel2-4.pdf}

}

\caption{plot model 2}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-pdf/plothat-1.pdf}

}

\caption{plot y hat}

\end{figure}%

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

\subsection{Third discussion point}\label{third-discussion-point}

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\subsection{Posterior predictive
check}\label{posterior-predictive-check}

\subsection{Diagnostics}\label{diagnostics}

\newpage

\section{References}\label{references}

\end{document}

### 2024-03-31 paper/sta302 project.Rmd
Add files via upload

---
title: "STA302 Project"
subtitle: "What factors and how influence Ames Iowa Housing Sale Price"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,message=FALSE,warning=FALSE}
library(MASS)
library(tidyverse)
library(magrittr)
library(gridExtra)
library(ggplot2)
library(car)
library(stargazer)
```

## Data

```{r}
current_dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
setwd(current_dir)
```

```{r}
ames_raw <- read.csv("../data/AmesHousing.csv")
```

```{r}
ames <- dplyr::select(ames_raw,`Central Air`, `Lot Shape`, `Garage Cars`, `Overall Qual`, `TotRms AbvGrd`, `Gr Liv Area`, `Garage Area`, `Fireplaces`, `SalePrice`)
ames <- na.omit(ames)
```

```{r}
rows <- sample(1:round(0.75*nrow(ames)), replace=FALSE) 
train<- ames[rows,]
test=ames[-rows,]
```

```{r}
summary(train[,-c(1,2)])
```

```{r}
### Categorical table
table(train$`Central Air`)
table(train$`Lot Shape`)
prop.table(table(train$`Central Air`))
prop.table(table(train$`Lot Shape`))
```

```{r}
summary(test[,-c(1,2)])
```

```{r}
table(test$`Central Air`)
table(test$`Lot Shape`)
prop.table(table(test$`Central Air`))
prop.table(table(test$`Lot Shape`))
```

## Visualization

```{r,fig.width=10,fig.height=12}
attach(train)
par(mfrow=c(4,2))
hist(SalePrice, breaks=10, main="",col="red")

hist(`Garage Area`, breaks=10, main="")
hist(`Gr Liv Area`, breaks=10, main="")

boxplot(`Overall Qual`, main = "",xlab="Overall Qual")
boxplot(`TotRms AbvGrd`, main = "",xlab="TotRms AbvGrd")

boxplot(`Fireplaces`, main = "",xlab="Fireplaces")

```

```{r,warning=FALSE,message=FALSE}
a=ggplot(data=train, aes(x=`Garage Area`, y=SalePrice)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE) + 
  labs(x = 'Garage Area', y='Sale Price')+
  theme_bw()

b=ggplot(data=train, aes(x=`Gr Liv Area`, y=SalePrice)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE) + 
  labs(x = 'Above grade (ground) living area square feet', y='Sale Price')+
  theme_bw()

grid.arrange(a,b, nrow=1)
```

## Model

```{r}
### Linear model full
full = lm(log(SalePrice) ~ ., data = train)
summary(full)
```

```{r}
m2 = lm(log(SalePrice) ~ .-`TotRms AbvGrd`, data = train)
summary(m2)
```

```{r}
# F test
anova(m2)
```

```{r}
m3 = lm(log(SalePrice) ~ `Central Air`+`Garage Cars`+`Overall Qual`+`Gr Liv Area`+`Garage Area`, data = train)
summary(m3)
```

```{r}
#Partial F test
anova(m2,m3)
```

Model checking

```{r,message=FALSE, echo=FALSE,warning=FALSE}
#condition 1
plot(train$SalePrice ~ exp(fitted(m2)), main="Y versus Y-hat", xlab="Y-hat", ylab="Y")
abline(a = 0, b = 1)
lines(lowess(train$SalePrice ~ exp(fitted(m2))), lty=2)
```

```{r,message=FALSE, echo=FALSE,warning=FALSE}
#condition 2
pairs(train[,-c(1,2)])
```

Model evaluation

```{r,message=FALSE, echo=FALSE,warning=FALSE}
par(mfrow=c(2,2))
plot(m2)
```

find outlier

```{r}
#find outlier
r <- rstandard(m2)
out <- which(r > 4 | r < -4)
out
```

```{r}
new_train = train[-out,]
```

```{r}
# determine whether there are leverage points
n <- nrow(new_train)
p <- length(coef(m2))-1
# leverage cutoff
h_cut <- 2*(p+1)/n 
off = which(hatvalues(m2) > h_cut)
off
```
```{r}
new_train = new_train[-off,]
```

```{r}
#cooks cutoff
D_cut <- qf(0.5, p+1, n-p-1)
which(cooks.distance(m2) > D_cut)
```

```{r}
#DFFITS cutoff
fits_cut <- 2*sqrt((p+1)/n) 
dff <- which(abs(dffits(m2)) > fits_cut)
dff
```
```{r}
new_train = new_train[-dff,]
```

```{r}
m4 = lm(log(SalePrice) ~ .-`TotRms AbvGrd`, data = new_train)
summary(m4)
```

```{r}
# F test
anova(m4)
```

Model checking

```{r,message=FALSE, echo=FALSE,warning=FALSE}
#condition 1
plot(new_train$SalePrice ~ exp(fitted(m4)), main="Y versus Y-hat", xlab="Y-hat", ylab="Y")
abline(a = 0, b = 1)
lines(lowess(new_train$SalePrice ~ exp(fitted(m4))), lty=2)
```

```{r,message=FALSE, echo=FALSE,warning=FALSE}
#condition 2
pairs(new_train[,-c(1,2)])
```

Model evaluation

```{r,message=FALSE, echo=FALSE,warning=FALSE}
par(mfrow=c(2,2))
plot(m4)
```

```{r}
r = resid(m4)
par(mfrow=c(1,3))
plot( r~ new_train$`Garage Area`, xlab="", ylab="residuals")
plot(r ~ new_train$`Garage Area`, xlab="", ylab="residuals")
qqnorm(r) 
qqline(r)
```

Multicollinearity test

```{r}
vif(m4)
```

```{r,warning=FALSE}
#export two models into one table. 
stargazer(full,m2,m3,m4, type="html",
          dep.var.labels=c("Log Sale Price"), out="train.htm")
```

The model checking for the validation model.

```{r,message=FALSE, echo=FALSE,warning=FALSE}
#model checking
m5=lm(log(SalePrice) ~ .-`TotRms AbvGrd`, data = test)
summary(m5)
```

```{r,message=FALSE, echo=FALSE,warning=FALSE}
par(mfrow=c(2,2))
plot(m5)
```

```{r,message=FALSE, echo=FALSE,warning=FALSE}
#model checking
r <- resid(m5)
# first check condition 1 and 2
#condition 1
plot(test$SalePrice ~ exp(fitted(m5)), main="Y versus Y-hat", xlab="Y-hat", ylab="Y")
abline(a = 0, b = 1)
lines(lowess(test$SalePrice ~ exp(fitted(m5))), lty=2)
```

```{r,message=FALSE, echo=FALSE,warning=FALSE}
#condition 2
# check conditions for checking model assumptions
pairs(test[,-c(1,2)])
```

```{r,warning=FALSE}
#export two models into one table. 
stargazer(m4,m5, type="html",
          dep.var.labels=c("Log Sale Price"), out="comp.htm")
```

### 2024-04-16 scripts/01-download_data.R
Add files via upload

@@ -1,0 +1,27 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+#library(opendatatoronto)
+library(ZillowR)
+library(tidyverse)
+# [...UPDATE THIS...]
+
+#### Download data ####
+# [...ADD CODE HERE TO DOWNLOAD...]
+
+
+
+#### Save data ####
+# [...UPDATE THIS...]
+# change the_raw_data to whatever name you assigned when you downloaded it.
+write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+
+         

### 2024-04-16 scripts/02-data_cleaning.R

@@ -1,0 +1,34 @@
+#### Preamble ####
+# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 6 April 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Clean data ####
+zillow <- read.csv("../data/analysis_data/zillow_price.csv")
+
+numeric_cols <- c('bathroomcnt',
+                  'bedroomcnt',
+                  'calculatedfinishedsquarefeet',
+                  'roomcnt',
+                  'yearbuilt',
+                  'taxvaluedollarcnt',
+                  'landtaxvaluedollarcnt',
+                  'price')
+
+zillowtrim <- zillow[, numeric_cols]
+
+
+
+zillowtrim <- na.omit(zillowtrim)
+
+
+
+#### Save data ####
+write.csv(zillowtrim,"../data/analysis_data/zillowtrim_analysis.csv",row.names = FALSE)

### 2024-04-16 scripts/04-model.R

@@ -1,0 +1,30 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+
+#### Read data ####
+analysis_data <- read_csv("../data/analysis_data/zillowtrim_analysis.csv")
+
+### Model data ####
+### full model
+full = lm(log(price) ~ ., data = train)
+summary(full)
+
+
+#### Save model ####
+saveRDS(
+  full,
+  file = "../models/full.rds"
+)
+
+

### 2024-04-17 paper/paper.qmd
Add files via upload

@@
 ---
-title: "STA302 Project"
-subtitle: "What factors and how influence Ames Iowa Housing Sale Price"
+title: "What factors and how influence Zillow Housing Sale Price"
 author: 
-  - First author
-  - Another author
+  - "Yaning Jin"
 thanks: "Code and data are available at: https://github.com/Yuki010305/Final-Paper."
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
-format: html
+abstract: "This project is interested in the factors affecting housing prices on zillow.
+After exploratory analysis of the data, a multiple linear regression was constructed, and a log transformation was performed to build a model with better performance.
+The transformed housing factors can explain more than 80% of the changes in housing prices.
+However, the existence of residuals in the model does not fully meet the constraints of the normality assumption, so in the future, data processing, feature engineering and model improvement are needed to study the factors affecting Zillow's housing prices.."
+format: pdf
 number-sections: true
 bibliography: references.bib
+link-citations: true
 ---
@@
 
+\tableofcontents
+
 # Introduction
 
-The housing issue is a pillar industry of a country, and the healthy development of the housing issue affects the country's economic development level.
-In order to help the stable development of the housing transaction market, this project plans to better evaluate the value of housing transactions for Ames.
-So, the main purpose of this project is to explore the factors that influence the sale price of homes in Ames, Iowa, and how they affect the home sales price.
-The characteristics of the homes we selected include central air condition, car capacity of garage, general shape of property, rate of overall quality, total above ground living area, number of fireplaces and sale year.
-The remainder of this paper is structured as follows.
-@sec-data....
+One of a nation's key industries is housing, and the health of this sector influences the degree of economic growth of the nation.
+A person's home is frequently the most expensive item in their life.
+Zillow is an online real estate database provider that assesses property values and offers details on the houses you're interested in [@loukissas2018all].
+The Zestimate prediction system was developed by Zillow.
+It is based on a data collection of hundreds of millions of homes and provides a preliminary estimate of a property's worth by combining a particular algorithm with the features of each home and the state of the market[@rolli2020zillow].
+To improve the accuracy of the Zestimate system and provide people with a more trustworthy way to estimate home prices, Zillow launched the Zillow Awards competition in 2017.
+Our goal in this project is not to participate in a competition to minimize the logarithmic error between the estimated house price and the actual selling price.
+The main purpose of our exploration in this project is to explore the factors that affect Zillow home sales prices and how they affect home sales prices.
+Characteristics of the homes we select include number of bathrooms, number of bedrooms, square footage, number of rooms, year, tax value, land tax value, etc.
 
@@
 ```{r}
-#| label: ames
-#| fig-cap: ames house
+#| label: Zillow
+#| fig-cap: Zillow house
 #| echo: false
-#current_dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
-#setwd(current_dir)
 
-ames_raw <- read.csv("../data/AmesHousing.csv")
+zillow <- read.csv("../data/analysis_data/zillow_price.csv")
 
@@
 
-The Raw data collects 82 features of the house, and data quality is not high.
+The Raw data collects 60 features of the house, and data quality is not high, there are many features with many null values, so 8 high-quality variables are selected from the variables for modeling and prediction.
 
 ```{r}
-#| label: ames select variable
-#| fig-cap: ames house save
+#| label: Zillow select variable
+#| fig-cap: Zillow house save
 #| echo: false
-ames <- dplyr::select(ames_raw,'Central.Air', 'Lot.Shape', 'Garage.Cars', 'Overall.Qual', 'TotRms.AbvGrd', 'Gr.Liv.Area', 'Garage.Area', 'Fireplaces','Yr.Sold', 'SalePrice')
-ames <- na.omit(ames)
 
-write.csv(ames,"../data/analysis_data/ames_analysis.csv",row.names = FALSE)
+numeric_cols <- c('bathroomcnt',
+                  'bedroomcnt',
+                  'calculatedfinishedsquarefeet',
+                  'roomcnt',
+                  'yearbuilt',
+                  'taxvaluedollarcnt',
+                  'landtaxvaluedollarcnt',
+                  'price')
+
+zillowtrim <- zillow[, numeric_cols]
+
+zillowtrim <- na.omit(zillowtrim)
+
+write.csv(zillowtrim,"../data/analysis_data/zillowtrim_analysis.csv",row.names = FALSE)
 
 ```
+
+|Variable|Description|
+|---|---|  
+|bathroomcnt|Number of bathrooms in home|   
+|bedroomcnt|Number of bedrooms in home|  
+|calculatedfinishedsquarefeet|Total finished living area of the home|  
+|roomcnt|Total number of rooms|  
+|yearbuilt|The Year the principal residence was built|  
+|taxvaluedollarcnt|The total tax assessed value of the parcel|  
+|landtaxvaluedollarcnt|The assessed value of the land area| 
+|price|price|
 
@@
 #| echo: false
-summary(ames[,-c(1,2)])
+summary(zillowtrim[,-c(1,2,4,5)])
 ```
 
-```{r}
+```{r,echo=FALSE,eval=FALSE}
 #| label: air
@@
 ### Categorical table
-table(ames$`Central.Air`)
-prop.table(table(ames$`Central.Air`))
+table(zillowtrim$bathroomcnt)
 ```
 
-```{r}
-#| label: lot
-#| fig-cap: lot shape table
+```{r,echo=FALSE,eval=FALSE}
+#| label: bedroomcnt
+#| fig-cap: bedroomcnt table
 #| echo: false
-table(ames$`Lot.Shape`)
-prop.table(table(ames$`Lot.Shape`))
+table(zillowtrim$bedroomcnt)
+prop.table(table(zillowtrim$bedroomcnt))
 ```
@@
 par(mfrow=c(1,2))
-hist(ames$SalePrice, breaks=10, xlab="Sale Price",main="Sale price",col="red") 
-hist(log(ames$SalePrice), breaks=10, xlab="log-transform Sale Price",main="Sale price",col="red") 
+hist(zillowtrim$price, breaks=10, xlab="Sale Price",main="Sale price",col="red") 
+hist(log(zillowtrim$price), breaks=10, xlab="log-transform Sale Price",main="Sale price",col="red") 
 ```
@@
 
-par(mfrow=c(3,2))
+par(mfrow=c(1,2))
 
-hist(ames$Garage.Area, breaks=10,main="", xlab="Garage Area")
-hist(ames$Gr.Liv.Area, breaks=10, main="",xlab="Above grade living area")
+hist(zillowtrim$bathroomcnt, breaks=10,main="", xlab="bathroom")
+hist(zillowtrim$bedroomcnt, breaks=10, main="",xlab="bedroom")
 
-boxplot(ames$Overall.Qual,xlab="Overall Qual")
-boxplot(ames$TotRms.AbvGrd, xlab="TotRms AbvGrd")
+par(mfrow=c(1,2))
+boxplot(zillowtrim$calculatedfinishedsquarefeet,xlab="square feet")
+boxplot(zillowtrim$roomcnt, xlab="room")
 
-boxplot(ames$Fireplaces, xlab="Fireplaces")
+par(mfrow=c(1,2))
+boxplot(zillowtrim$taxvaluedollarcnt, xlab="tax value")
+boxplot(zillowtrim$landtaxvaluedollarcnt, xlab="land tax value")
 ```
 
-```{r,warning=FALSE}
+```{r,warning=FALSE,message=FALSE}
 #| label: point
@@
 #| echo: false
-a=ggplot(data=ames, aes(x=Garage.Area, y=SalePrice)) + 
+a=ggplot(data=zillowtrim, aes(x=bathroomcnt, y=price)) + 
   geom_point() + 
   geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
-  labs(x = 'Garage Area', y='Sale Price')+
+  labs(x = 'bathroom', y='Sale Price')+
   theme_bw()
 
-b=ggplot(data=ames, aes(x=Gr.Liv.Area, y=SalePrice)) + 
+b=ggplot(data=zillowtrim, aes(x=taxvaluedollarcnt, y=price)) + 
   geom_point() + 
   geom_smooth(method = lm, se = FALSE,size=1.5) + 
-  labs(x = 'Above grade living area square feet', y='Sale Price')+
+  labs(x = 'tax value', y='Sale Price')+
   theme_bw()
@@
 
-The above scatter plot shows that both Garage Area and Above grade living area have a certain positive impact on sale price, especially the positive correlation between Above grade living area and sale price is very strong.
+The above scatter plot shows that tax value has a certain positive impact on sale price, the positive correlation between tax value and sale price is very strong.
+
+```{r,warning=FALSE,message=FALSE}
+#| label: point1
+#| fig-cap: points1
+#| echo: false
+a=ggplot(data=zillowtrim, aes(x=calculatedfinishedsquarefeet, y=price)) + 
+  geom_point() + 
+  geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
+  labs(x = 'square feet', y='Sale Price')+
+  theme_bw()
+
+b=ggplot(data=zillowtrim, aes(x=bedroomcnt, y=price)) + 
+  geom_point() + 
+  geom_smooth(method = lm, se = FALSE,size=1.5) + 
+  labs(x = 'bedroom', y='Sale Price')+
+  theme_bw()
+
+grid.arrange(a,b, nrow=1)
+```
+
+The above scatter plot shows that square feet has a certain positive impact on sale price, the positive correlation between square feet and sale price is very strong.
 
@@
 set.seed(123456)
-rows <- sample(1:round(0.75*nrow(ames)), replace=FALSE) 
-train<- ames[rows,]
-test=ames[-rows,]
+rows <- sample(1:round(0.75*nrow(zillowtrim)), replace=FALSE) 
+train<- zillowtrim[rows,]
+test=zillowtrim[-rows,]
 ```
@@
 ### full model
-full = lm(log(SalePrice) ~ ., data = train)
+full = lm(log(price) ~ ., data = train)
 summary(full)
@@
 #| 
-ml = lm(log(SalePrice) ~ .-TotRms.AbvGrd-Yr.Sold, data = train)
-summary(ml)
+log_ml = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = train)
+summary(log_ml)
 ```
@@
 ```{r}
-#| label: ftest
-#| fig-cap: F test
+#| label: savebestmodel
+#| fig-cap: save besr model
 #| echo: false
-
-# F test
-anova(ml,full)
+#| 
+saveRDS(log_ml , "../models/best_model.rds")
 ```
-
-Analyzing the model of full and significant variables through the Partial F test, we found that the p value is much greater than 0, which shows that we cannot reject the null hypothesis and there is not much difference in the performance of the two models.
-But in terms of the number of variables, we still choose the model with significant variables.
 
@@
 #| echo: false
-par(mfrow=c(2,2))
+#par(mfrow=c(2,2))
 
-plot(ml)
+#plot(log_ml)
 ```
@@
 n <- nrow(train)
-p <- length(coef(ml))-1
+p <- length(coef(log_ml))-1
 # leverage cutoff
 h_cut <- 2*(p+1)/n 
-off = which(hatvalues(ml) > h_cut)
+off = which(hatvalues(log_ml) > h_cut)
 new_train = train[-off,]
@@
 #| 
-ml_new = lm(log(SalePrice) ~ .-TotRms.AbvGrd-Yr.Sold, data =new_train)
+ml_new = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = new_train)
 summary(ml_new)
@@
 #| 
-saveRDS(ml_new, "../model/model.rds")
+saveRDS(ml_new, "../models/model.rds")
 ```
@@
 #| echo: false
-par(mfrow=c(2,2))
 plot(ml_new)
@@
 #| 
-plot(new_train$SalePrice ~ exp(fitted(ml_new)), main="Y versus Y-hat", xlab="Y-hat", ylab="Y")
+plot(new_train$price ~ exp(fitted(ml_new)), main="Y versus Y-hat", xlab="Y-hat", ylab="Y")
 abline(a = 0, b = 1)
-lines(lowess(new_train$SalePrice ~ exp(fitted(ml_new))), lty=2)
+lines(lowess(new_train$price ~ exp(fitted(ml_new))), lty=2)
 ```
@@
 
+the errors are independent.
+
 #### A3.Common Error variance
 
-homoskedasticity
+the errors have constant variance.
 
@@
 
+```{r}
+#| label: plotqq
+#| fig-cap: plot qq
+#| echo: false
+#| 
+qqnorm(resid(ml_new))
+qqline(resid(ml_new))
+```
+
 # Results
 
-```{r}
-#| echo: false
-#| label: read
-#| eval: true
-#| warning: false
-#| message: false
+Estimating the value of a home is a common difficulty.
+Therefore, a lot of work has already been completed.
+Lee [@lee2016software] make an effort to develop multivariate regression models based on house datasets and assess the models using maximum information coefficient statistics based on anticipated values and home prices.
+When a moderate to big data sample size is employed, Nghiep et al.
+[@nguyen2001predicting] examined two methods: multiple regression analysis (MRA) and artificial neural networks (ANN).
+Based on the prediction performance, ANN performs better than MRA.
+An artificial neural network (ANN) model was created after Limsombunchai [@limsombunchao2004house
+] that ANNs are more accurate in predicting property values than hedonic regression models.
 
-library(rstanarm)
-
-model <-
-  readRDS(file = ("../model/model.rds"))
-
-summary(model)
-#stargazer(model, type="latex",
-#          dep.var.labels=c("Log Sale Price"), align = TRUE)
-```
-
-1. When other factors remain unchanged, having central air conditioning increases the sales price of a house by 16.22%.
+The final model shows that the number of bathrooms, bedrooms, rooms, year taxes and fees of the building, square feet, etc.
+all have a significant impact on Zillow’s housing prices.For every additional bathroom, the house price increases by 1.017% per unit.
+For every additional bedroom, the house price actually decreases by 0.01%.
+In addition, the newer the building is, the housing prices actually decrease.
+For every 1% unit increase in taxes and fees, housing prices increase by 0.67% unit.These findings explain the relationship between house-related attributes and house prices.
 
@@
 
-## First discussion point {#sec-first-point}
-
-## Second discussion point
-
-## Third discussion point
-
 ## Weaknesses and next steps
 
-Weaknesses and next steps should also be included.
+However, the residuals of our model do not fully satisfy the normality assumption.
+Such violations may reduce the model's predictive accuracy on new data sets.
+Another limitation of this model is that transforming the data makes the model less interpretable.
+
+To start making these models better in the future, divide each training dataset into smaller training tests and perform some cross-validation before generating the test files.
+This might enhance performance, or at the very least increase the predictability of the model's output.
+Although most categorical variables cannot be included in the model because of memory and time restrictions when running the model, the model may be enhanced with improved feature engineering.
+These variables can be included in the model by being divided into smaller groups.
+Making some interactive words is an additional thought.
+It is crucial to classify missing variables as predictors once all missing values have been imputed, as was previously noted.
 
@@
 
-# Appendix {.unnumbered}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-## Diagnostics
-
 \newpage

### 2024-04-17 paper/paper.qmd
Add files via upload

@@
   - "Yaning Jin"
-thanks: "Code and data are available at: https://github.com/Yuki010305/Final-Paper."
+thanks: "Code and data are available at: https://github.com/Yuki010305/What-factors-and-how-influence-Zillow-Housing-Sale-Price.git."
 date: today
@@
 library(tidyverse)
-library(MASS)
-library(magrittr)
 library(gridExtra)
 library(ggplot2)
-library(car)
 library(stargazer)
+library(xtable)
 library(modelsummary)
+library(kableExtra)
+library(tinytex)
 
@@
 Characteristics of the homes we select include number of bathrooms, number of bedrooms, square footage, number of rooms, year, tax value, land tax value, etc.
+The estimated model is
+
+$$\text{log(price)}=\beta_0+\beta_1\text{bathrooms}+\beta_2\text{log(squarefootage)}+...+\beta_6\text{taxValue}$$
+For some variables we will also do some log transformations.
 
@@
 
+## Raw Data
+
+In this research, we examine zillow data sourced using the zillbowR library [@rolli2020zillow].
+The dataset encompasses 90,275 records (89,499 records after cleaning), focusing on specific variables: bathroom number, bedroom number, year built, square feet, room number, tax value, etc.
+The apartments were built in a wide range of years, from as early as 1885 to as recently as 2015.
+
 The Raw data collects 60 features of the house, and data quality is not high, there are many features with many null values, so 8 high-quality variables are selected from the variables for modeling and prediction.
+
+## Data Analysis tools
+
+R [@citeR], a potent open-source statistical programming language, was used to analyze the data.
+To improve the effectiveness of our data operations, we used a collection of R packages from the tidyverse [@citetidyverse], which is a collection of tools created for data science.
+The `dplyr` package [@rDplyr] offered a consistent collection of verbs that aid in filtering, summarizing, and organizing the dataset, while the `ggplot2` package [@rGgplot2] made it easier to create complex visualizations.
+Because of its quick and user-friendly data reading capabilities, the `readr` package [@rReadr] was used.
+`Knitr` [@rKnitr] handled report production dynamically, allowing R code to be included into this document.
+`kableExtra`[@R-kableExtra] was also used to create visually appealing and editable tables, which improved the way our results were presented.
 
@@
 
+## Variable Description {#sec-variable}
+
 |Variable|Description|
@@
 
+# Exploratory Data Analysis {#sec-exploration}
+
 ```{r}
@@
 #| echo: false
-summary(zillowtrim[,-c(1,2,4,5)])
+#summary(zillowtrim[,-c(1,2,4,5)])
+
+#kableExtra::kable(t(zillowtrim[,-c(1,2,4,5)]), format="latex")
 ```
@@
 ### Categorical table
-table(zillowtrim$bathroomcnt)
+table(zillowtrim$yearbuilt)
 ```
@@
 
-par(mfrow=c(1,2))
+#par(mfrow=c(1,2))
 
-hist(zillowtrim$bathroomcnt, breaks=10,main="", xlab="bathroom")
-hist(zillowtrim$bedroomcnt, breaks=10, main="",xlab="bedroom")
+#hist(zillowtrim$calculatedfinishedsquarefeet, breaks=10,main="", xlab="square feet")
+#boxplot(zillowtrim$taxvaluedollarcnt, xlab="tax value")
+#hist(zillowtrim$bedroomcnt, breaks=10, main="",xlab="bedroom")
 
-par(mfrow=c(1,2))
-boxplot(zillowtrim$calculatedfinishedsquarefeet,xlab="square feet")
-boxplot(zillowtrim$roomcnt, xlab="room")
+#par(mfrow=c(1,2))
+#boxplot(zillowtrim$calculatedfinishedsquarefeet,xlab="square feet")
+#boxplot(zillowtrim$roomcnt, xlab="room")
 
-par(mfrow=c(1,2))
-boxplot(zillowtrim$taxvaluedollarcnt, xlab="tax value")
-boxplot(zillowtrim$landtaxvaluedollarcnt, xlab="land tax value")
+#par(mfrow=c(1,2))
+#boxplot(zillowtrim$taxvaluedollarcnt, xlab="tax value")
+#boxplot(zillowtrim$landtaxvaluedollarcnt, xlab="land tax value")
 ```
@@
 #| echo: false
-a=ggplot(data=zillowtrim, aes(x=bathroomcnt, y=price)) + 
+#a=ggplot(data=zillowtrim, aes(x=bathroomcnt, y=price)) + 
+#  geom_point() + 
+#  geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
+#  labs(x = 'bathroom', y='Sale Price')+
+#  theme_bw()
+
+#b=ggplot(data=zillowtrim, aes(x=taxvaluedollarcnt, y=price)) + 
+#  geom_point() + 
+#  geom_smooth(method = lm, se = FALSE,size=1.5) + 
+#  labs(x = 'tax value', y='Sale Price')+
+#  theme_bw()
+
+#grid.arrange(a,b, nrow=1)
+```
+
+```{r,warning=FALSE,message=FALSE}
+#| label: point1
+#| fig-cap: points1
+#| echo: false
+a=ggplot(data=zillowtrim, aes(x=calculatedfinishedsquarefeet, y=price)) + 
   geom_point() + 
   geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
-  labs(x = 'bathroom', y='Sale Price')+
+  labs(x = 'square feet', y='Sale Price')+
   theme_bw()
@@
 The above scatter plot shows that tax value has a certain positive impact on sale price, the positive correlation between tax value and sale price is very strong.
-
-```{r,warning=FALSE,message=FALSE}
-#| label: point1
-#| fig-cap: points1
-#| echo: false
-a=ggplot(data=zillowtrim, aes(x=calculatedfinishedsquarefeet, y=price)) + 
-  geom_point() + 
-  geom_smooth(method = lm, se = FALSE,size=1.5,color="red") + 
-  labs(x = 'square feet', y='Sale Price')+
-  theme_bw()
-
-b=ggplot(data=zillowtrim, aes(x=bedroomcnt, y=price)) + 
-  geom_point() + 
-  geom_smooth(method = lm, se = FALSE,size=1.5) + 
-  labs(x = 'bedroom', y='Sale Price')+
-  theme_bw()
-
-grid.arrange(a,b, nrow=1)
-```
 
@@
 full = lm(log(price) ~ ., data = train)
-summary(full)
+#summary(full)
 ```
@@
 log_ml = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = train)
-summary(log_ml)
+#summary(log_ml)
 ```
@@
 #par(mfrow=c(2,2))
-
 #plot(log_ml)
@@
 summary(ml_new)
+#latex_code <- stargazer(full, log_ml, ml_new,type = "latex", title = "Regression Results" ,align = TRUE)
+#cat(latex_code, file = "regression_results.tex")
+#xelatex("regression_results.tex")
 ```
@@
 #| echo: false
-plot(ml_new)
+#plot(ml_new)
 ```
@@
 #### A2.Covariance of Errors
+
+```{r}
+#| label: plotresidual
+#| fig-cap: plot resid
+#| echo: false
+#| 
+plot(ml_new, which=1)
+
+```
 

### 2024-04-17 other/datasheet/datasheet.qmd
Add files via upload

---
title: "What factors and how influence Zillow Housing Sale Price"
author: "Yaning Jin "
thanks: "Code and data are available at: https://github.com/Yuki010305/What-factors-and-how-influence-Zillow-Housing-Sale-Price.git"
date: today
date-format: long
abstract: "This project is interested in the factors affecting housing prices on zillow. After exploratory analysis of the data, a multiple linear regression was constructed, and a log transformation was performed to build a model with better performance. The transformed housing factors can explain more than 80% of the changes in housing prices. However, the existence of residuals in the model does not fully meet the constraints of the normality assumption, so in the future, data processing, feature engineering and model improvement are needed to study the factors affecting Zillow’s housing prices.."
format: pdf
number-sections: true
bibliography: references.bib
link-citations: true
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - This dataset was created to study the factors that affect Zillow home prices, with a focus on determining how factors such as bathroom, square footage, tax value, etc. affect Zillow home prices.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by Zillow as data of kaggle competition.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The dataset creation was funded by Zillow.
4. *Any other comments?*
	- N/A

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances represent evaluations of zillow houses and their selling prices, including their bathroom number, bedroom number.
2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 90,275 instances in the dataset.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of year 2016 zillow of all houses sold. The representativeness of the sample.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of features such as the bedroom number, tax value, year built and price et al.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- The target variable is price, which indicates zillow sales price.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Some instances may have missing information due to incomplete records or unavailability of data at the time of evaluation.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- The dataset does not explicitly make relationships between individual instances.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- specific data splits are recommended for this dataset. And use the test set to evaluate the model.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The dataset may contain errors or noise due to inaccuracies in the evaluation process or inconsistencies in record-keeping.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- No.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No.
16. *Any other comments?*
	- No.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data for each instance was obtained through zillow, an airbnb property sales organization. This information is observable and is reported by zillow. This data was then validated to ensure accuracy and reliability.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data collection involved administrative procedures by zillow to ensure consistent and valid data collection.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset is not a sample but a comprehensive collection of evaluations from the zillow in year 2016.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The data collection was conducted by zillow. No additional compensation was provided for data collection as it falls under their regular job responsibilities.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was collected over 2016.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- While specific ethical review processes for this dataset are not mentioned, it is assumed that zillow to follow standard for data collection, ensuring compliance with legal and ethical standards, information will not be matched to specific houses.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected directly by Zillow, so I collected it directly from the person involved.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	-  This is a public data source and the persons concerned will not be notified about the data collection.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The dataset does not involve personal data, so there is no mechanism for individuals to revoke consent for the use of this data as it is part of regulatory compliance.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- An impact analysis specifically for this dataset was not described.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- Additional comments or concerns regarding the data collection process can be directed to zillow Open Data through the contact information provided on the portal, and mobile phone verification is required before collection.
12. *Any other comments?*
	- No.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes, the dataset was preprocessed and cleaned. Since many of our 60 features contain a large number of missing values, in order to ensure the completeness and reliability of the analysis, I only selected 8 key factors with relatively few missing values as predictor variables.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The original raw dataset remains stored in its initial directory labeled 'data/raw_data' within our project repository. This allows for reference or re-analysis should future research require access to the unprocessed information.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The software used for preprocessing, namely the R programming language along with packages 'readr', 'dplyr', is publicly available.
4. *Any other comments?*
	- Following the cleaning process, we only retained the essential columns necessary for our analysis to streamline the dataset and focus on the variables of interest. The filtered dataset with these columns is available for review and further analysis, ensuring transparency and reproducibility of our study.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is distributed to the public, which allows for both commercial and non-commercial use without restrictions.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset can be downloaded directly from kaggle. While there is no mention of a DOI, the portal provides a direct download link for the dataset.
3. *When will the dataset be distributed?*
	- The dataset is already available for distribution as it is posted on the open data portal.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- As mentioned, the dataset allows for worldwide, royalty-free, and perpetual use.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	-  No additional IP-based restrictions from third parties are imposed on the data, but you need to verify your mobile phone number to participate in the competition before you can download the data.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- For any additional questions or comments about the dataset, the Open Data team can be reached via their contact details on the portal.
7. *Any other comments?*
	- No

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- zillow's data team will be responsible for supporting, hosting and maintaining the dataset.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The Open Data team can be contacted through the official Open Data portal.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- Any errata or updates to the dataset are likely to be communicated through zillow, where users can find the latest information and corrections.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset will not be updated and is historical sales data.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- This dataset primarily relates to house, so it does not directly pertain to individuals. Therefore, retention limits specific to personal data may not be applicable.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the dataset may be archived and accessible through the Open Data Portal.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- While zillow encourages the use of open data to help improve its models, contributions to official datasets are generally the responsibility of its data team. Any extensions or contributions need to be coordinated with the Open Data team and can only contribute to the missing filling of their data.
8. *Any other comments?*
	- No.

\newpage

# References

### 2024-04-17 scripts/00-simulate_data.R
Add files via upload

@@ -1,19 +1,40 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Data sets related to simulating the impact of different factors on house prices
+# Author:Yaning Jin
+# Date: 16 April 2024
+# Contact: jinyaning010305@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: tidyverse package
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
+# Load necessary libraries
+library(tidyverse)
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+# Set seed for reproducibility
+set.seed(123)
 
+# Number of observations
+n <- 1000
 
+# Simulate data
+data <- tibble(
+  house_size = rnorm(n, mean = 2000, sd = 500),
+  num_bedrooms = sample(1:5, n, replace = TRUE),
+  distance_to_center = rnorm(n, mean = 10, sd = 5),
+  other_factor = rnorm(n)  # Add more factors as needed
+)
+
+# Simulate house prices based on factors
+data <- data %>%
+  mutate(
+    house_price = 100000 + 100 * house_size + 20000 * num_bedrooms - 500 * distance_to_center + rnorm(n, mean = 0, sd = 10000)
+    # Add more factors to the formula as needed
+  )
+
+# View the simulated data
+head(data)
 

### 2024-04-17 scripts/01-download_data.R

@@ -1,27 +1,37 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: To download and preprocess the dataset related to building evaluation from the zillow
+# Author: Yaning Jin
+# Date: 16 April 2024
+# Contact: jinyaning010305@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: The 'zillowR' package for accessing open data, 'readr' and 'dplyr' for data manipulation, and 'here' for path management
+# Ensure that the 'zillowR' package is installed and updated to the latest version
+
 
 
 #### Workspace setup ####
 #library(opendatatoronto)
 library(ZillowR)
 library(tidyverse)
+library(readabs)
 # [...UPDATE THIS...]
 
 #### Download data ####
 # [...ADD CODE HERE TO DOWNLOAD...]
 
+#GetZestimate(
+#  zpid = NULL,
+#  rentzestimate = FALSE,
+#  zws_id = getOption("ZillowR-zws_id"),
+#  url = "http://www.zillow.com/webservice/GetZestimate.htm"
+#)
+the_raw_data <- read_abs("6401.0", tables = "9", check_local=FALSE) %>%
+  filter(str_detect(`series`, "Health"))
 
 
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+write_csv(the_raw_data, "../raw_data.csv") 
 
          

### 2024-04-17 scripts/02-data_cleaning.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Clean building assessment data by removing NA values ​​and analyze factors affecting housing prices
+# Author: Yaning Jin
+# Date: 16 April 2024
+# Contact: jinyaning010305@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 'readr' for reading CSV data, 'dplyr' for data manipulation, and 'here' for managing file paths
+# The raw dataset must be located in the 'data/raw_data' directory before running this scrip
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-04-17 scripts/03-test_data.R

@@ -1,15 +1,42 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Conduct a series of data integrity tests on the cleaned dataset of factors affecting house prices
+# Author: Yaning Jin
+# Date: 16  2024
+# Contact: jinyaning010305@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: 'readr' for reading CSV data, 'dplyr' for data manipulation, 'here' for file path management
+# The cleaned dataset should be located in the 'data/analysis_data' directory and be free of processing errors
 
 #### Workspace setup ####
 library(tidyverse)
 # [...UPDATE THIS...]
 
+
+
+data <- read.csv("../data/analysis_data/zillowtrim_analysis.csv")
+
 #### Test data ####
+# Dimension Check
+dim(data)  # Check the number of rows and columns in the dataset
+
+# Missing Values Check
+any(is.na(data))  # Check if there are any missing values in the dataset
+
+# Duplicate Rows Check
+data_unique <- unique(data)  # Remove duplicate rows
+duplicate_count <- nrow(data) - nrow(data_unique)
+if (duplicate_count > 0) {
+  print(paste("Duplicate rows found:", duplicate_count))
+}
+
+# Consistency Check
+str(data)  # Check the structure of the dataset for consistency in data types
+
+# Outlier Check (assuming 'price' is the target variable)
+summary(data$price)  # Summary statistics of the 'price' variable to identify outliers
+
+
+
+
+
+

### 2024-04-17 scripts/04-model.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Construct multiple linear regression to evaluate the impact of different factors on housing prices
+# Author: Yaning Jin
+# Date: 16 April 2024
+# Contact: jinyaning010305@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: The 'readr' for data manipulation, and 'here' for path management
+# The 'cleaned_data' dataset must be pre-processed before using it in the model.
 
 
 #### Workspace setup ####

### 2024-04-17 scripts/05-replications.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Replicated graphs from
+# Author: Yaning Jin
+# Date: 16 April 2024
+# Contact: jinyaning010305@gmail.com
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: The 'readr' for data manipulation, and 'here' for path management
+# The 'cleaned_data' dataset must be pre-processed before using it in the model.
 
 
 #### Workspace setup ####
@@ -14,6 +14,31 @@ library(tidyverse)
 
 #### Load data ####
 # [...ADD CODE HERE...]
+
+#### Read data ####
+analysis_data <- read_csv("../data/analysis_data/zillowtrim_analysis.csv")
+
+#### Replicate Graphs ####
+
+# Example 1: Scatter plot of 'price' against 'calculatedfinishedsquarefeet'
+ggplot(analysis_data, aes(x = calculatedfinishedsquarefeet, y = price)) +
+  geom_point() +
+  labs(title = "Scatter plot of Price against Sqft",
+       x = "Sqft",
+       y = "Price")
+
+# Example 2: Histogram of 'price'
+ggplot(analysis_data, aes(x = price)) +
+  geom_histogram( fill = "skyblue", color = "black") +
+  labs(title = "Histogram of Price",
+       x = "Price",
+       y = "Frequency")
+
+# Add more plots as needed
+
+# Remember to customize the plots according to your specific requirements
+
+
 
 
 

### 2024-04-17 other/datasheet/datasheet.qmd
Add files via upload

@@
 ---
-title: "What factors and how influence Zillow Housing Sale Price"
+title: "Zillow House Price Predict Analysis"
 author: "Yaning Jin "
-thanks: "Code and data are available at: https://github.com/Yuki010305/What-factors-and-how-influence-Zillow-Housing-Sale-Price.git"
+thanks: "Code and data are available at: https://github.com/Yuki010305/Zillow-House-Price-Predict-Analysis.git"
 date: today

### 2024-04-17 paper/paper.qmd
Add files via upload

@@
 ---
-title: "What factors and how influence Zillow Housing Sale Price"
+title: "Zillow House Price Predict Analysis"
 author: 
   - "Yaning Jin"
-thanks: "Code and data are available at: https://github.com/Yuki010305/What-factors-and-how-influence-Zillow-Housing-Sale-Price.git."
+thanks: "Code and data are available at: https://github.com/Yuki010305/Zillow-House-Price-Predict-Analysis.git."
 date: today
@@
 
+## Measurement
+
+In this study, we leveraged data from the Zillow dataset, accessed through the Zillow API.
+The Zillow dataset provides comprehensive information on residential properties, enabling analyzes focused on housing market dynamics, property valuation, and spatial characteristics.
+
+The Zillow dataset encompasses various attributes crucial for understanding residential properties' characteristics and market behavior. Specifically:
+
+bathroomcnt: Indicates the number of bathrooms present in each residential property, influencing its utility and convenience for occupants.
+bedroomcnt: Represents the count of bedrooms within each residential unit, influencing its suitability for different household compositions.
+calculatedfinishedsquarefeet: Quantifies the total finished living area of the home, reflecting its size and spatial configuration.
+roomcnt: Denotes the total number of rooms in the residential unit, encompassing living spaces, bedrooms, and other functional areas, providing insights into the property's layout.
+yearbuilt: Specifies the year in which the principal residence was constructed, offering insights into the age distribution of properties within the dataset.
+taxvaluedollarcnt: Indicates the total tax-assessed value of the parcel, serving as a key indicator of property valuation for taxation purposes.
+landtaxvaluedollarcnt: Reflects the assessed value of the land area associated with each residential parcel, contributing to the overall property valuation.
+price: Represents the price of the residential property, serving as a fundamental metric for market valuation and investment analysis.
+By analyzing these attributes, researchers can gain valuable insights into housing market trends, property valuation factors, and the impact of various features on real estate prices within the studied area.
+
+To ensure the dataset's suitability for analysis, we performed several preprocessing steps.
+Select high-quality variables with few missing values and remove missing values.
+Additionally, we implemented data cleaning procedures to exclude observations with missing values, ensuring the completeness and reliability of our dataset for subsequent analyses.
+
+For detailed descriptions of each variable, please refer to the table provided in Section @sec-variable.
+
 # Exploratory Data Analysis {#sec-exploration}
@@
 
-```{r}
-#| label: histprice
-#| fig-cap: sale price hist
+```{r }
+#| label: fig-histprice
+#| fig-cap: sale price and log sale price hist
 #| echo: false
@@
 ```
-
-As you can see from the figure, house sales prices are right-skewed data. When building the model, we need to log-transform the house sales prices to make them conform to the normal distribution.
+@fig-histprice, house sales prices are right-skewed data. When building the model, we need to log-transform the house sales prices to make them conform to the normal distribution.
 
@@
 ```{r,warning=FALSE,message=FALSE}
-#| label: point1
-#| fig-cap: points1
+#| label: fig-pointstwo
+#| fig-cap: Bivariate visualization
 #| echo: false
@@
 
-The above scatter plot shows that tax value has a certain positive impact on sale price, the positive correlation between tax value and sale price is very strong.
-
-The above scatter plot shows that square feet has a certain positive impact on sale price, the positive correlation between square feet and sale price is very strong.
+@fig-pointstwo shows that tax value has a certain positive impact on sale price, the positive correlation between tax value and sale price is very strong.
+@fig-pointstwo also shows that square feet has a certain positive impact on sale price, the positive correlation between square feet and sale price is very strong.
 
@@
 ml_new = lm(log(price) ~ bathroomcnt+bedroomcnt+log(calculatedfinishedsquarefeet)+roomcnt+yearbuilt+log(taxvaluedollarcnt)+log(landtaxvaluedollarcnt), data = new_train)
-summary(ml_new)
+#summary(ml_new)
 #latex_code <- stargazer(full, log_ml, ml_new,type = "latex", title = "Regression Results" ,align = TRUE)
@@
 
-Clearly the model has improved.
-
 #### A1:Linearity of the Relationship
@@
 ```{r}
-#| label: plothat
-#| fig-cap: plot y hat
+#| label: fig-plothat
+#| fig-cap: Y versus Y-hat 
 #| echo: false
@@
 
-The above scatter plot fits the relationship between the predicted value and the actual value.
+@fig-plothat fits the relationship between the predicted value and the actual value.
 You can see that these points are almost on or close to the line, so we can say that a linear relationship is satisfied.
@@
 ```{r}
-#| label: plotresidual
-#| fig-cap: plot resid
+#| label: fig-plotresidual
+#| fig-cap: Residual Plot
 #| echo: false
@@
 
-the errors are independent.
+The residual plot @fig-plotresidual does not show any pattern, we can conclude that the residual terms are independently distributed across different predicted value ranges, consistent with the independence assumption of linear regression analysis.
 
@@
 
-the errors have constant variance.
+The residual plot @fig-plotresidual is not a uniform distribution. As the predicted value increases, the variance decreases, so the assumption of constant variance is not completely established.
 
@@
 ```{r}
-#| label: plotqq
-#| fig-cap: plot qq
+#| label: fig-plotqq
+#| fig-cap: Normal Q-Q plot
 #| echo: false
-#| 
 qqnorm(resid(ml_new))
@@
 ```
+
+There are obvious deviations at both ends of the QQ graph @fig-plotqq, which may indicate that the data does not conform to the normal distribution in this area.
 
@@
 
+The final model is:
+
+$$
+\begin{aligned}
+log(price) &=2.7-0.007bathroomcnt -0.006 bedroomcnt -0.2 log(squarefeet) \\ 
+    &-0.015 roomcnt -0.00025 yearbuilt + 0.67log(taxvaluedollarcnt) -0.055 log(landtaxvaluedollarcnt)
+\end{aligned}
+$$
+
+Adjusted R-squared is 0.8082, indicating that the model can explain approximately 80.83% of the variance of the target variable (logarithm of house prices).
+
 The final model shows that the number of bathrooms, bedrooms, rooms, year taxes and fees of the building, square feet, etc.
-all have a significant impact on Zillow’s housing prices.For every additional bathroom, the house price increases by 1.017% per unit.
+all have a significant impact on Zillow’s housing prices.
+For every additional bathroom, the house price increases by 1.017% per unit.
 For every additional bedroom, the house price actually decreases by 0.01%.
@@
 # Discussion
+
+## Discussion
+
+**Model Interpretability and Generalization**
+While the developed model provides valuable insights into the factors influencing housing prices, its interpretability is hindered by the transformation of data and the exclusion of certain categorical variables due to memory and time constraints.
+To address this, future research could explore methods to maintain model interpretability while optimizing predictive performance.
+Techniques such as feature selection and dimensionality reduction may help streamline the model without sacrificing interpretability.
+
+**Addressing Residual Normality Assumption**
+The observed violations of the normality assumption in the model's residuals raise concerns regarding its robustness and generalizability.
+To mitigate this issue, researchers could explore alternative modeling approaches or employ robust regression techniques that are less sensitive to deviations from normality.
+Additionally, conducting thorough diagnostic checks and sensitivity analyses can help identify potential sources of bias and improve the model's reliability.
+
+**Enhancing Model Performance Through Cross-Validation**
+The suggestion to partition training datasets into smaller subsets and perform cross-validation before generating test files holds promise for improving model performance and generalization.
+By systematically evaluating the model's performance across different subsets of data, researchers can gain insights into its stability and identify areas for refinement.
+Implementing rigorous cross-validation protocols can also enhance the model's credibility and ensure its applicability across diverse datasets.
+
+**Future Directions in Feature Engineering**
+Future iterations of the model could benefit from more sophisticated feature engineering techniques aimed at capturing the nuanced relationships between housing attributes and prices.
+Exploring advanced feature transformation methods, such as polynomial features or interaction terms, may help uncover hidden patterns and improve the model's predictive accuracy.
+Additionally, incorporating domain knowledge and expert insights into the feature selection process can enrich the model's explanatory power and enhance its utility for real-world applications.
+
+**Handling Missing Data**
+Addressing missing data is critical for ensuring the reliability and validity of the model's predictions.
+Researchers should carefully consider imputation strategies and explore techniques for incorporating missing variables as predictors in the model.
+By systematically addressing missing data issues, researchers can enhance the model's robustness and improve its performance on new datasets.
+
+In summary, while the developed model provides valuable insights into the factors influencing housing prices, there are several avenues for future research to enhance its interpretability, robustness, and predictive accuracy.
+By addressing these challenges and leveraging advanced modeling techniques, researchers can develop more reliable and actionable models for estimating housing values.
 

### 2024-04-17 scripts/01-download_data.R
Add files via upload

@@ -14,10 +14,8 @@
 library(ZillowR)
 library(tidyverse)
 library(readabs)
-# [...UPDATE THIS...]
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
 
 #GetZestimate(
 #  zpid = NULL,
@@ -30,7 +28,6 @@ the_raw_data <- read_abs("6401.0", tables = "9", check_local=FALSE) %>%
 
 
 #### Save data ####
-# [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(the_raw_data, "../raw_data.csv") 
 

### 2024-04-17 scripts/02-data_cleaning.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Clean building assessment data by removing NA values ​​and analyze factors affecting housing prices
+# Purpose: Clean building assessment data by removing NA values and analyze factors affecting housing prices
 # Author: Yaning Jin
 # Date: 16 April 2024
 # Contact: jinyaning010305@gmail.com

### 2024-04-17 scripts/03-test_data.R

@@ -9,9 +9,6 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
-
-
 
 data <- read.csv("../data/analysis_data/zillowtrim_analysis.csv")
 

### 2024-04-17 scripts/05-replications.R

@@ -10,12 +10,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Load data ####
-# [...ADD CODE HERE...]
-
-#### Read data ####
 analysis_data <- read_csv("../data/analysis_data/zillowtrim_analysis.csv")
 
 #### Replicate Graphs ####

### 2024-04-17 paper/paper.qmd
Add files via upload

@@
 format: pdf
+toc: true
+toc-depth: 2
 number-sections: true
@@
 ```
-
-\tableofcontents
 
